UMD Building Classification

### 2024-12-09 report/paper/draft.tex
draft final final check

From these prior works we have the basic motivation of leveraging traditional CNN image segmentation and recognition techniques for the sake of identifying any buildings in the input images. Our main innovation is to attempt to use Grad-CAM++ or a similar technique to see if they can be used for image segmentation instead, and to attempt to apply this basic system to a variety of goals.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.8\linewidth]{fixmatch.png}
    \caption{FixMatch Model Grad-CAM visualization}
    \label{fig:fixmatch_results}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[trim={0 38cm 0 12.5cm},clip,width=0.6\linewidth]{meanteacher.png}
    \caption{MeanTeacher Model Grad-CAM visualization}
    \label{fig:meanteacher_results}
\end{figure}
% Demonstrate stats

@@

@@

Note how in the pictures, excessive complexity is granted to largely irrelevant details, such as the clouds and sky. Minute differences in the image data due to noise result in a lack of clustering in those areas.

>>>>

From these prior works we have the basic motivation of leveraging traditional CNN image recognition techniques for the sake of identifying any buildings in the input images. Our main innovation is to attempt to use Grad-CAM++ or a similar technique to see if they can be used for helping improve recognition instead, and to attempt to apply this basic system to a variety of goals.

We use Grad-CAM because we need a way to visualize the convolutional layers to help guide a semi-supervised model. If we look at the Fully Connected (FC) layers, the feature maps get flattened into a 1-D vector, which loses the spatial information inherent in the earlier convolutional layers, so it is not the place we should be looking for. Grad-CAM is thus a method of visualizing the convolutional layers, and can be used to help guide the model to focus on the building itself.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=0.6\linewidth]{fixmatch.png}
    \caption{FixMatch Model Grad-CAM visualization}
    \label{fig:fixmatch_results}
\end{figure}

@@

\begin{figure}[H]
    \centering
    \includegraphics[trim={0 38cm 0 12.7cm},clip,width=0.6\linewidth]{meanteacher.png}
    \caption{MeanTeacher Model Grad-CAM visualization}
    \label{fig:meanteacher_results}
\end{figure}
% Demonstrate stats

@@

\subsection*{Presentation}

A presentation of this project is available at: \url{https://docs.google.com/presentation/d/1SDHgrbd2Suk2Qw0XBbqwSBKSYyZ87k4XBCzELvPUu8c/edit?usp=sharing}

@@
